---
title: "Interactive County Census Analysis and Map Visualization"
format: html
self-contained: true
    toc: true
    toc-location: left
editor: visual
---

## Introduction

Here I will provide a walk through of an interactive county census analysis and map visualization for Washington state.

### Steps: 

These are all the packages needed for the interactive county census analysis and map visualization.

```{r}setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Turn off scientific notation
options(scipen=999)

# Load the tidyverse.
library(tidyverse)
library(tidycensus)
library(leaflet.extras2)
library(glue)
library(mapview)
library(tmap)

```

This is the api key I used to access the census data. You can make your own on https://api.census.gov/data/key_signup.html 
```{r echo=FALSE}

myapikey <- "fc489a837248834b523a1eab369df67966f37652"

tidycensus::census_api_key(myapikey, overwrite=TRUE, install = TRUE)
```

Then I need to identify my variables, which are the total population and the population in poverty.
```{r}
myvars <- c(totalpop = "B01003_001",
            povertystatus = "B05010_001")
```




```{r}

```

